---
title: "Week2"
author: "Marcelo Gomes Gadelha"
date: "18/09/2019"
output: html_document
---

## Week 2 - Data Science Capstone

### Libraries and basic configuration

```{r package_instance}

  #install.packages("tm") 
  #install.packages("NLP")
  library("NLP")
  library("tm")
  source("functions.R")

  dir = "final/en_US/"

```

### Exploratory Analysis

Instructions 

    Exploratory analysis - perform a thorough exploratory analysis of the data, understanding the distribution of words and relationship between the words in the corpora.
    Understand frequencies of words and word pairs - build figures and tables to understand variation in the frequencies of words and word pairs in the data.

    1. Some words are more frequent than others - what are the distributions of word frequencies?
    2. What are the frequencies of 2-grams and 3-grams in the dataset?
    3. How many unique words do you need in a frequency sorted dictionary to cover 50% of all word instances in the language? 90%?
    4. How do you evaluate how many of the words come from foreign languages?
    5. Can you think of a way to increase the coverage -- identifying words that may not be in the corpora or using a smaller number of words in the dictionary to 
    6. cover the same number of phrases?
    
### Read Data
```{r reading_data}

blogs_en   <- readLines("final/en_US/en_US.blogs.txt",  encoding = "UTF-8")
news_en    <- readLines("final/en_US/en_US.news.txt", encoding = "UTF-8")
twitter_en <- readLines("final/en_US/en_US.twitter.txt", encoding = "UTF-8")

```

### Set seed, sampleing, and clean data and Sampleing
```{r cleannig_data}

set.seed(1000)

qtd_sample    <- 100
t_blogs_en    <- sample(blogs_en, qtd_sample)
t_news_en     <- sample(news_en, qtd_sample)
t_twitter_en  <- sample(twitter_en, qtd_sample)


```

## 1. Some words are more frequent than others - what are the distributions of word frequencies?


```{r question_1}

1

```

## 2. What are the frequencies of 2-grams and 3-grams in the dataset?


```{r question_2}

2

```

## 3. How many unique words do you need in a frequency sorted dictionary to cover 50% of all word instances in the language? 90%?


```{r question_3}

3

```

## 4. How do you evaluate how many of the words come from foreign languages?


```{r question_4}

5

```

## 5. Can you think of a way to increase the coverage -- identifying words that may not be in the corpora or using a smaller number of words in the dictionary to 


```{r question_5}

5

```

## 6. cover the same number of phrases?

```{r question_6}

6

```

### Modeling

Instructions:

Questions to consider

    1. How can you efficiently store an n-gram model (think Markov Chains)?
    2. How can you use the knowledge about word frequencies to make your model smaller and more efficient?
    3. How many parameters do you need (i.e. how big is n in your n-gram model)?
    4. Can you think of simple ways to "smooth" the probabilities (think about giving all n-grams a non-zero probability even if they aren't observed in the data) ?
    5. How do you evaluate whether your model is any good?
    6. How can you use backoff models to estimate the probability of unobserved n-grams?
    
    
    
```{r }

2+2

```
    
    
    
    
    
    
    